---
title: "Pre-Labeling's Initial Protocol"
author:
  - name: Jose Storopoli
date: "Created on 19/03/2021 updated on `r format(Sys.time(), '%d/%m/%Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 6,
                      fig.asp = 0.618,
                      out.width = "70%",
                      fig.align = "center",
                      fig.retina = 3)
```

## Data

Read all the CSV files from Liverpool's data. We have a total of 2,535,916 tweets! I have no idea what are `undefined_col`, `undefined_col2` and `undefined_col3`. The CSV file doesn't came with a header row and twitter's API docs are inconclusive. We need Liverpool's help to figure this out.

```{r read-data}
library(dplyr, warn.conflicts = FALSE)
library(vroom)

df <- vroom("~/Desktop/flu_pt_raw_tweets.csv",
    col_names = c("index", "id", "created_at", "text", "user",
                  "place", "user_place", "country", "coordinates",
                  "undefined_col", "undefined_col2", "undefined_col3"),
    col_types = "ffTcfccc?cii",
    na = c("", "NA", "None"),
    locale = locale(date_format = "y-m-d H:M:S"))
df
```

Coordinates less than 5% complete data.

```{r skim-data}
library(skimr, warn.conflicts = FALSE)
skim(df)
```

## Sample randomly 1k tweets

We need to shuffle the data and extract 1k random tweets for the students to cross-label:

```{r sample_data}
library(readr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
set.seed(123)
sample_df <- df %>%
    drop_na(text) %>%
    sample_n(1e3)
sample_df %>% write_csv("sample_1k.csv")
```

## Session Information

```{r SessionInfo}
sessionInfo()
```
